Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-16 paper/ms.tex
update ms (wip)

\appendix
\section{Cases With ``Inconsistent'' Rotation and Lithium-Based Ages}
\label{app:inconsistent}

>>>>

\appendix
\section{Literature Age Scale Comparison}
\label{app:litagecomparison}

Figure~\ref{fig:agescalecompone}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{NGC6811_lit_ages_vs_cluster_ages.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{Cep-Her_lit_ages_vs_cluster_ages.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{NGC6819_lit_ages_vs_cluster_ages.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{Melange3_lit_ages_vs_cluster_ages.pdf}
	 	}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{Theia520_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Age scale comparison (part 1).}  
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
    lorem ipsum dolur. 
	}
	\label{fig:agescalecompone}
\end{figure*}

\section{Cases With ``Inconsistent'' Rotation and Lithium-Based Ages}
\label{app:inconsistent}
